Supporting Information for ``Seniority and hierarchy configuration interaction for radicals and excited states''

### 2023-08-20 Manuscript/manuscript.tex
sup

Equilibrium geometries of ethylene and vinyl; details about the fitting of potential energy curves;
potential energy curves for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
computed according to FCI and the various hCI, eCI, and sCI models considered here;
and convergence of the NPE, distance errors, and equilibrium properties of
open-shell (\ce{OH}, \ce{CN}, vinyl, and \ce{H7})
and closed-shell (\ce{HF}, \ce{F2}, ethylene, \ce{N2}, \ce{H4}, and \ce{H8}) systems,
as a function of the number of determinants, according to the various CI models considered here while
corrected with the standard and the renormalized EN2 perturbative energy.

>>>>

Equilibrium geometries of ethylene and vinyl; details about the fitting of potential energy curves;
potential energy curves for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
computed according to FCI and the various hCI, eCI, and sCI models considered here;
and convergence of the NPE, distance errors, and equilibrium properties of
open-shell (\ce{OH}, \ce{CN}, vinyl, and \ce{H7})
and closed-shell (\ce{HF}, \ce{F2}, ethylene, \ce{N2}, \ce{H4}, and \ce{H8}) systems,
as functions of the number of determinants, according to the various CI models considered here while
corrected with the standard and the renormalized EN2 perturbative energy.

### 2023-08-20 Manuscript/sup.tex
sup

%%% FIG S1 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes}
\caption{
Potential energy curves for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
according to hCI (green), excitation-based CI (red) and sCI (blue) models.
}
\label{fig:plot_pes}
\end{figure*}
%%% %%% %%%

%%% FIG S3 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes_closed}
\caption{
Potential energy curves for \ce{HF}, \ce{F2}, \ce{N2}, ethylene, \ce{H4}, and \ce{H8},
according to hCI (green), excitation-based CI (red) and sCI (blue) models,
with (light tones) and without (dark tones) the EN2 perturbative correction.
Results first reported in Ref. \onlinecite{Kossoski_2022}.
}
\label{fig:plot_pes_closed}
\end{figure*}
%%% %%% %%%

>>>>

%%% FIG S1 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes}
\caption{
Potential energy curves for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
according to FCI (black), hCI (green) (dashed lines for half-integer $h$), eCI (red), and sCI (blue) models, with the cc-pVDZ basis set and frozen-core approximation.}
\label{fig:plot_pes}
\end{figure*}
%%% %%% %%%

%%% FIG S2 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_OH}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for \ce{OH},
as a function of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_oh}
\end{figure*}
%%% %%% %%%

%%% FIG S3 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_CN}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for \ce{CN},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_cn}
\end{figure*}
%%% %%% %%%

%%% FIG S4 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_vinyl}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for vinyl,
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_vinyl}
\end{figure*}
%%% %%% %%%

%%% FIG S5 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_H7}
\caption{
\label{fig:plot_pt2_rpt2_h7}
Non-parallelity error (NPE), distance error, equilibrium distance, and force constant, for \ce{H7},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\end{figure*}
%%% %%% %%%

%%% FIG S6 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_HF}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for \ce{HF},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_hf}
\end{figure*}
%%% %%% %%%

%%% FIG S7 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_F2}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for \ce{F2},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_f2}
\end{figure*}
%%% %%% %%%

%%% FIG S8 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_ethylene}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for ethylene,
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_ethylene}
\end{figure*}
%%% %%% %%%

%%% FIG S9 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_N2}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and vibrational frequency, for \ce{N2},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_n2}
\end{figure*}
%%% %%% %%%

%%% FIG S10 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_H4}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and force constant, for \ce{H4},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_h4}
\end{figure*}
%%% %%% %%%

%%% FIG S11 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pt2_rpt2_H8}
\caption{
Non-parallelity error (NPE), distance error, equilibrium distance, and force constant, for \ce{H8},
as functions of the number of determinants ($\Ndet$), according to hCI (green), eCI (red) and sCI (blue) models,
with the standard (full lines with circles) and renormalized (dashed lines with triangles) EN2 perturbative correction.
The dashed lines represent the FCI results.}
\label{fig:plot_pt2_rpt2_h8}
\end{figure*}
%%% %%% %%%
